\section{Background}\label{sec:background}

Research into railway operations gained significant traction in the middle of the twentieth century, when such papers as 
\textit{A Model for the Optimal Programming of Railway Freight Train Movements} in 1956 \cite{chamil56a} and 
\textit{Timetables for a Suburban Rail Transit System} in 1969 \cite{salzborn69a} 
sought to formalize problems in the domain by appealing to fields such as management science and linear programming.
Over the following decades, the railway operations literature grew as researchers explored solutions involving 
dynamic programming and branch and bound procedures \cite{petmer81a}, 
integer programming and heuristics \cite{caigoh94a}, 
Lagrangian relaxation \cite{brlinoni98a}, among others.

In recent years, large railway operators have kept an open mind to novel approaches in 
machine learning, artificial intelligence, and other academic disciplines
as potential solutions to a growing number of problems in transportation.
In 2019, the Swiss Federal Railway (SBB), founded the Flatland Challenge \cite{monylascscbhwaegeibavistsasp20a},
a global online railway scheduling and rescheduling competition
in search of efficient ways of managing dense railway traffic.
While the organizers have shown a particular interest in reinforcement learning and imitation learning solutions,
they have kept an open mind toward a wider array of approaches.

Answer set programming has already demonstrated success with problems in similar domains, such as 
multi-agent pathfinding \cite{ngobsoscye21a}, 
scheduling problems \cite{bainkaokscsotawa19a} \cite{elgesc22a}, and
traffic management \cite{tamava25a}.
Pathfinding is a key component of railway planning,
and given that multiple trains share a common network with the mandate to find collision-free paths to their goals,
one can view this as a multi-agent pathfinding problem.
Similarly, since trains may be expected to follow a fixed timetable,
one can view this as a scheduling problem, 
in which certain events must occur in a particular order or deadlines must be respected.
Furthermore, the execution of railway activity may deviate from its intended plan, leading to congestion and delays.
In this way, the central management of railway operations resembles the problem of urban traffic control.

In fact, answer set programming has even already been proven to work on railway-specific problems.
The hybrid system \textit{clingo}[DL] has been used to successfully create train schedules 
over a period of six hours for a portion of Switzerland containing hundreds of train lines
in a matter of minutes \cite{abjoossctowa21a}.


%
%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: "paper"
%%% End:
