\section{Research goals}\label{sec:goal}

The goal of this research is to establish best practices for modeling large railway systems in answer set programming.
In short, this can be seen in three phases:
\begin{enumerate}
	\item Formalization of railway environments
	\item Solutions to the Flatland problem
	\item Application to real challenges 
\end{enumerate}
	
\subsection{Formalization}
Our initial goal has been to formally understand large railway systems.
By leveraging the Flatland ecosystem
as a virtual railway generator and simulator,
we have obtained an end-to-end view
over a large sample of environments.
This means we have been able to 
consider a large diversity of characteristics in environments
and iteratively test and refine our formal definitions.
Additionally, developing a comprehensive formalization
has enabled us to better relate the problems in modeling railway systems 
to those encountered in similar domains.
%as well as initial encodings, 

\subsection{Solution}
Following this, the aim is to exhaustively solve the Flatland problem,
which necessitates a solution to both the 
vehicle scheduling problem (VSP) and
the vehicle rescheduling problem (VRSP).
Described in more detail in Section~\ref{sec:issues},
the extension into VRSP requires the ability to handle
stochastic malfunctions,
which represent breakdowns and delays that occur every day
in real railway networks.
VSP instances take place during the operational planning phase
and since these occur ahead of time,
we can be more forgiving about how long it takes to find an acceptable solution.
VRSP instances take place in response to unforeseen events,
and since the surrounding conditions can change in real time,
preference is given to finding a solution quickly
over finding an optimal solution.

Furthermore, the quantitative evaluation of encodings
gives us an idea of how ASP-based approaches compare to machine learning
and other similar approaches.
However, is not strictly necessary that the encodings outperform high-ranking
encodings from the competition,
as answer set programming provides important guarantees that other approaches do not,
for example the avoidance of deadlocks and collisions,
and that all trains reach their goals.

Finally, solving the Flatland problem requires
accounting for trains that move at various speeds.
The speed characteristic was initially included to simulate the discrepancies between
fast-moving intercity trains and slow-moving local or freight trains.
This concept has already been explored in our encodings,
but is yet to be finalized.

\subsection{Application}
Beyond just Flatland, this body of understanding can be translated to critical problems faced by railway operators.
Narayanaswami and Rangaraj classify problems in railway operations into broad categories from planning to execution \cite{narran2011a}.
Specific problems from across that spectrum that are worth addressing include
\begin{itemize}
	\item routing and scheduling
	\item preemptive replanning for adverse events
	\item valid switch position logic (such as that used by the ILTIS system)
	\item energy utilization
	\item route synchronization
	\item modeling speed and acceleration
	\item personnel management
	\item rolling stock management
	\item maintenance scheduling
\end{itemize}
Although solutions to many issues in the realm of transportation are rooted in public policy,
it is my hope that this research can contribute to the solving of problems that require or can benefit from technological solutions.

%
%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: "paper"
%%% End:
