\section{Current status}\label{sec:status}

We have submitted to ASPOCP 2026 a paper titled \textit{Flaspland: A Test-bed for Routing and Scheduling in Answer Set Programming}.
This paper 
provides a comprehensive formalization of the railway scheduling problem posed by Flatland,
explores alternative formal representations of railway environments,
and reviews experimental results on a variety of pathfinding encodings.
For the following iteration of this paper, 
we have begun exploring encodings that leverage optimization and difference logic.

Beyond the most recent paper, I continue to maintain and improve the toolkit introduced in Secton~\ref{sec:introduction} 
known as \textit{Flaspland}.
It serves as a bridge between the open-source Flatland code, which is written in Python, and answer set programming encodings written in clingo.
There is a two-step asynchronous process.
In the first step, an environment is generated from user-defined specifications and is converted into a clingo fact representation file.
In the second step, the output of a pathfinding encoding (or set of encodings) is converted into a Python object that Flatland recognizes.
Since the toolkit adheres to a common fact format, developers are free to explore various techniques and styles of encodings.
Altogether, this allows for the seamless development, testing, debugging, and presentation of a wide variety of solutions.

In practice, the formalization outlined in the paper and the \textit{Flaspland} toolkit are used by the students in our \textit{Railway Scheduling} course at Universit\"at Potsdam.
We update the course each semester to provide them with the latest view of this research,
and in turn the topics the students pursue in the course contribute to our broader understanding of modeling railway systems in answer set programming.

%
%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: "paper"
%%% End:
