\documentclass[]{include/latex-class-ceurart/ceurart}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{microtype}
\usepackage{url}\urlstyle{tt}
\usepackage{bm}
\usepackage{wrapfig}
\begin{document}

\section*{Personal Statement}
Dear Committee of the 22\textsuperscript{nd} Doctoral Consortium on Logic Programming,
\bigskip

\noindent
I believe that the story of how we move is the story of who we are.
\medskip

\noindent
My name is Ryan Kepler James Murphy,
a Ph.D. student supervised by Prof. Dr. Torsten Schaub
at Universit\"at Potsdam in Germany
within the Institute of Computer Science.
I am currently in my second year of studies
with the Knowledge Representation and Reasoning (KRR) group,
where my research applies answer set programming to large railway systems. 
I apply techniques from
multi-agent pathfinding,
temporal logic,
and reasoning under uncertainty
to problems faced by large railway operators
such as
routing,
vehicle scheduling, and
vehicle rescheduling.
My ambition has always been to find a way to have a meaningful impact
on society, and I hope my research can be a path to do that.
\medskip

\noindent
I would be honored to take part in the 22\textsuperscript{nd} Doctoral Consortium,
as this would be my first opportunity to get feedback in such a large and varied setting.
I place value both on learning from those with experience and
understanding work from an interdisciplinary perspective.
And I believe that success comes from humility and collaboration.
This would be a wonderful opportunity to grow, 
as well as to learn how contribute to the success of others.
Thanks in advance for your time and consideration,
and I wish all the best with the organization and execution of this year's events.

\bigskip
\bigskip
\noindent
Best regards,

\bigskip
\bigskip
\bigskip
\bigskip
\noindent
Ryan Kepler James Murphy

\end{document}
